Scalar on Function Regression

### 2022-01-01 Presentation/slides.tex
Some slide stuff

>>>>

	\begin{frame}{Principal Component Analysis}
		Setting: $Y = X\beta + \epsilon$ \: with standardized regressors in $X$ \\
		Goal: \textbf{Dimension Reduction} 
		\vspace{0.3cm}

		Let $\Sigma_X = Cov(x)$ and let $\{\lambda_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvalues} of $\Sigma_X$ and $\{\gamma_i\}_{i \in \mathcal{I}}$ be the \textbf{Eigenvectors} of $\Sigma_X$.
	\end{frame}

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}

		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]$$

		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]$$

		The \textbf{Eigenvalues} and \textbf{Eigenfunctions}: $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$  are solutions of the following equation:
		$$ \int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t) $$
	\end{frame}

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
		A random function $F$ can be expressed in terms of its mean function and its Eigenfunctions:
		$$F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$

		Where the $\xi_j$ are scalar-valued random variables with variance $\lambda_j$.\\
		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
	\end{frame}
